Supplement to Automatic Matching of Bullet Lands

### 2016-04-27 imaging-paper.Rnw
Merge the set44 with the regular set

\subsection{Algorithm}\label{sec:algorithm}
<<twolands100, cache=TRUE,  echo=FALSE>>=
images <- file.path(datadir, dir(datadir))

@@

<<twolands100adjust, echo=FALSE>>=
images <- file.path(datadir, dir(datadir))

@@

\begin{figure}[hbtp]
  \centering
<<crosscuts-vary-b31, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100,250, by=25)
lof <- processBullets(read.x3p(paths[37]), name = paths[37], x = crosscuts)
lof$bullet <- paste(scrubPath(lof$bullet), lof$x)

@@

\begin{figure}[hbtp]
  \centering
<<tree, echo=FALSE, fig.width=7, fig.height=4, out.width='.7\\textwidth'>>=
library(rpart)
library(rpart.plot)
library(RColorBrewer)
vals = alpha(brewer.pal(3, name="Paired"), alpha=0.5)
names(bstats)[9:10] <- c("#matches", "#non-matches")
includesVar <- setdiff(names(bstats), c("b1", "b2", "data", "resID", "id.x", "id.y", "pred", "forest", "bullet", "span", "crosscutdist", "flagged", "km"))
cc <- read.csv("csvs/crosscuts-25.csv")
# cc$bullet <- gsub(".*//","",cc$path)
# cc$bullet <- gsub(".x3p", "", cc$bullet)
# bstats$flagged <- bstats$b2 %in% cc$bullet[which(is.na(cc$cc))] |
#                   bstats$b1 %in% cc$bullet[which(is.na(cc$cc))]

>>>>

\subsection{Algorithm}\label{sec:algorithm}
<<twolands100, cache=TRUE,  echo=FALSE>>=
images <- file.path(datadir, dir(datadir))
images <- images[grep(" ", images)]

@@

<<twolands100adjust, echo=FALSE>>=
images <- file.path(datadir, dir(datadir))
images <- images[grep(" ", images)]

@@

\begin{figure}[hbtp]
  \centering
<<crosscuts-vary-b31, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
paths <- paths[grep(" ", paths)]

crosscuts <- seq(100,250, by=25)
lof <- processBullets(read.x3p(paths[37]), name = paths[37], x = crosscuts)
lof$bullet <- paste(scrubPath(lof$bullet), lof$x)

@@

\begin{figure}[hbtp]
  \centering
<<tree, echo=FALSE, fig.width=7, fig.height=4, out.width='.7\\textwidth'>>=
library(rpart)
library(rpart.plot)
library(RColorBrewer)
vals = alpha(brewer.pal(3, name="Paired"), alpha=0.5)
names(bstats)[9:10] <- c("#matches", "#non-matches")
includesVar <- setdiff(names(bstats), c("b1", "b2", "data", "resID", "id.x", "id.y", "pred", "forest", "bullet", "span", "crosscutdist", "flagged", "km"))
#cc <- read.csv("csvs/crosscuts-25.csv")
# cc$bullet <- gsub(".*//","",cc$path)
# cc$bullet <- gsub(".x3p", "", cc$bullet)
# bstats$flagged <- bstats$b2 %in% cc$bullet[which(is.na(cc$cc))] |
#                   bstats$b1 %in% cc$bullet[which(is.na(cc$cc))]

### 2016-04-27 imaging-supplement.Rnw
Merge the set44 with the regular set

paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100, 400, by = 50)
lof <- processBullets(read.x3p(paths[5]), name = scrubPath(paths[5]), x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

# match unknown land using crosscuts
ccs <- read.csv("csvs/crosscuts-25.csv")
all_bullets <- lapply(as.character(ccs$path), function(x) {
  result <- read.x3p(x)
  result[[3]] <- x
  names(result)[3] <- "path"

@@

%\hh{XXX maybe use log of D to remove the left boundary XXX}
<<allhamby, echo=FALSE, message=FALSE, warning=FALSE>>=
knowndatadir <- "app/images/Hamby252_3DX3P1of2/"
knowns <- dir(path=knowndatadir)
knowns <- gsub(".x3p", "", knowns)

unknowndatadir <- "app/images/Hamby252_3DX3P2of2/"
unknowns <- dir(path=unknowndatadir)
unknowns <- gsub(".x3p", "", unknowns)

@@

<<aligned, echo=FALSE, warning=FALSE,  cache=TRUE>>=
matches <- read.csv("csvs/matches.csv", header = FALSE)
matches$barrel <- rep(1:10, each=6)
matches$id <- 1:nrow(matches)
library(reshape2)
mm <- melt(matches, id.var=c("barrel", "id"), na.rm=TRUE)
mm <- subset(mm, value != "")
mm$value <- gsub("Br.* Bullet ", "", mm$value)
mm$prefix <- sprintf("Br%d Bullet ", mm$barrel)
unkns <- grep("[A-Z]",mm$value)
mm$prefix[unkns] <- "Ukn Bullet "
mm$path <- "app/images/Hamby252_3DX3P1of2//"
mm$path[unkns] <- "app/images/Hamby252_3DX3P2of2//"
mm$path <-   with(mm, paste0(path, prefix, value, ".x3p"))

ccs <- read.csv("csvs/crosscuts-25.csv")
mm <- merge(mm, ccs, by="path", all=TRUE)
mm <- subset(mm, !is.na(mm$cc))

>>>>

paths <- file.path(datadir, dir(datadir))
paths <- paths[grep(" ", paths)]

crosscuts <- seq(100, 400, by = 50)
lof <- processBullets(read.x3p(paths[5]), name = scrubPath(paths[5]), x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

# match unknown land using crosscuts
ccs <- read.csv("csvs/crosscuts-25-old.csv")
all_bullets <- lapply(as.character(ccs$path), function(x) {
  result <- read.x3p(x)
  result[[3]] <- x
  names(result)[3] <- "path"

@@

%\hh{XXX maybe use log of D to remove the left boundary XXX}
<<allhamby, echo=FALSE, message=FALSE, warning=FALSE>>=
knowndatadir <- "app/images/Hamby252_3DX3P1of2/"
knowns <- dir(path=knowndatadir)
knowns <- knowns[grep(" ", knowns)]
knowns <- gsub(".x3p", "", knowns)

unknowndatadir <- "app/images/Hamby252_3DX3P2of2/"
unknowns <- dir(path=unknowndatadir)
unknowns <- unknowns[grep(" ", unknowns)]
unknowns <- gsub(".x3p", "", unknowns)

@@

<<aligned, echo=FALSE, warning=FALSE,  cache=TRUE>>=
matches <- read.csv("csvs/matches-old.csv", header = FALSE)
matches$barrel <- rep(1:10, each=6)
matches$id <- 1:nrow(matches)
library(reshape2)
mm <- melt(matches, id.var=c("barrel", "id"), na.rm=TRUE)
mm <- subset(mm, value != "")
mm$value <- gsub("Br.* Bullet ", "", mm$value)
mm$prefix <- sprintf("Br%d Bullet ", mm$barrel)
unkns <- grep("[A-Z]",mm$value)
mm$prefix[unkns] <- "Ukn Bullet "
mm$path <- "app/images/Hamby252_3DX3P1of2//"
mm$path[unkns] <- "app/images/Hamby252_3DX3P2of2//"
mm$path <-   with(mm, paste0(path, prefix, value, ".x3p"))

ccs <- read.csv("csvs/crosscuts-25-old.csv")
mm <- merge(mm, ccs, by="path", all=TRUE)
mm <- subset(mm, !is.na(mm$cc))
